Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-13 ccppabc/text/revision/main.tex
2PCF restriction sentence removed from abstract
Issue #17 (Ref Report comment 3) dealt with

% Abstract of the paper
\begin{abstract}
{\bf \color{dred}
Standard approaches to Bayesian parameter inference in large scale 
structure assume a Gaussian functional form (chi-squared form) 
for the likelihood. They are also limited to analyzing measurements of   
the two-point correlation function. These restrictions, in detail, cannot 
be correct. Likelihood free inferences such as Approximate Bayesian Computation (ABC) 
relax these restrictions and make inference possible without making any 
assumptions on the likelihood.
} 
Instead it relies on a forward generative model of the data and a metric 
for measuring the distance between the model and data. In this work, we 
demonstrate that ABC is feasible for LSS parameter inference by using it 
to constrain parameters of the halo occupation distribution (HOD) model 
for populating dark matter halos with galaxies.

@@

%It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC.  Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects.  This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.
{\bf \color{dred} 
These selection effects, coupled with the systematic effects earlier this section, 
make correctly predicting the functional form of the likelihood intractable.
In the standard Gaussian pseudo-likelihood analysis, and other analysis that
require writing down a likelihood function, these effects can significantly 
bias the inferred parameter constraints. In these situations, employing
ABC equipped with a generative forward model that incorproates selection and 
systematic effects may produce less biased parameter constraints. 
}
%Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
%\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.

>>>>

% Abstract of the paper
\begin{abstract}
{\bf \color{dred}
Standard approaches to Bayesian parameter inference in large scale 
structure assume a Gaussian functional form (chi-squared form) 
for the likelihood. This assumption, in detail, cannot %They are also limited to analyzing measurements of the two-point correlation function. 
be correct. Likelihood free inferences such as Approximate Bayesian Computation (ABC) 
relax these restrictions and make inference possible without making any 
assumptions on the likelihood.
} 
Instead it relies on a forward generative model of the data and a metric 
for measuring the distance between the model and data. In this work, we 
demonstrate that ABC is feasible for LSS parameter inference by using it 
to constrain parameters of the halo occupation distribution (HOD) model 
for populating dark matter halos with galaxies.

@@

%It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC.  Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects.  This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.
{\bf \color{dred} 
These selection effects, coupled with the systematic effects earlier this section, 
make correctly predicting the likelihood intractable. In the standard Gaussian 
pseudo-likelihood analysis, and other analysis that require writing down a 
likelihood function, these effects can significantly 
bias the inferred parameter constraints. In these situations, employing
ABC equipped with a generative forward model that incorproates selection and 
systematic effects may produce less biased parameter constraints. 
}
%Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
%\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.
